---
title: "Aides Drug"
author: "Syi-yonnie Richard"
date: "September 23, 2021"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
triUmp <-read.csv(file="triUmpsal.csv",header=TRUE)
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

A new  preventative aides drug (triUmpsal) is under test in clinical trials. Consider only the females, does this drug seem effective?  Hint - use dplyr to obtain that subpopulation with the filter command.

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->
We need the results and percentage for just females data.
```{r}
females<-filter(triUmp,gender=="F")
```


# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

```{r}
barchartGC(~infected + treatment,data=females)
barchartGC(~infected + treatment,data=females, type="percent")

```

While analyzing this chart, we can see that the drug percentage of that women used forced a negative impact on their health in catching aids. While analyzing the placebo chart, women taking the placebo prescription had a more positive chance in not catching aids. All in all, women with the drug received a more negative feedback than the women who took the placebo (Women who took the drug about 59% & women who took the placebo about 52%.

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
table1 <- xtabs(~infected + treatment, data=females)
rowPerc(table1)
colPerc(table1)
```

While Analyzing the data, we can see each infection percentage between the women who take drugs vs placebo as a treatment. Around 58% of women were infected using a drug prescribed while women who take placebo were estimated around 41% which shows placebo would help more than the drug prescription.
## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

While analyzing this section, there's a analysis from a person and the fisher test. The "persons" observed count results shows 210/5,484 were treated using the drug prescription, while, 147/5,927 were treated with using the placebo, this shows a 63% semi-positive difference between the both users. According to the counts by null, 172/5,521 were treated using the drug, while, 184/5,889 were treated using the placebo which is a more positive result between the both. The chi-sq statistic 8.04 shows the drugs treated women & 7.54 women prescribed placebo were treated, showing, a positive impact from both medications. A big difference was shown from both the person's test results and the fisher results.

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variables causes the other, or whether they perhaps are related for some other reason.  Watch the chapter 6 videos from the George-town videos collection.!-->

While working on WUP_5 we were able to observe each analysis of women who used the prescription of drugs as a treatment for aids vs the women who used placebo as a treatment for drugs. Both women using either treatment had some type of results of treatment, but, women using at the end of the analysis using the drug had a better chance of treatment than the women using placebo. The drug had rounded up to a positive percentage of 3.9% while placebo users estimated up to 3.3%,showing a 5% difference between how to drugs can treat women infection.